%%%%%%%%%%%%%%%%%
% This is an example CV created using altacv.cls (v1.1, 21 November 2016) written by
% LianTze Lim (liantze@gmail.com), based on the 
% Cv created by BusinessInsider at http://www.businessinsider.my/a-sample-resume-for-marissa-mayer-2016-7/?r=US&IR=T
% 
%% It may be distributed and/or modified under the
%% conditions of the LaTeX Project Public License, either version 1.3
%% of this license or (at your option) any later version.
%% The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.3 or later is part of all distributions of LaTeX
%% version 2003/12/01 or later.
%%%%%%%%%%%%%%%%

%% If you want to use \orcid or the
%% academicons icons, add "academicons"
%% to the \documentclass options. 
%% Then compile with XeLaTeX or LuaLaTeX.
% \documentclass[10pt,a4paper,academicons]{altacv}
% \documentclass[11pt,a4paper,sans]{moderncv}
\documentclass[10pt,a4paper]{altacv}

%% AltaCV uses the fontawesome and academicon fonts
%% and packages. 
%% See texdoc.net/pkg/fontawecome and http://texdoc.net/pkg/academicons for full list of symbols.
%% When using the "academicons" option,
%% Compile with LuaLaTeX for best results. If you
%% want to use XeLaTeX, you may need to install
%% Academicons.ttf in your operating system's font %% folder.


% Change the page layout if you need to
\geometry{left=1cm,right=9cm,marginparwidth=6.8cm,marginparsep=1.2cm,top=1cm,bottom=1cm}

% Change the font if you want to.

% If using pdflatex:
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[default]{lato}
% \usepackage{fontspec}
% \setmainfont{Ubuntu Mono}
\usepackage{hyperref}

% If using xelatex or lualatex:
% \setmainfont{Lato}

% Change the colours if you want to
% 3E0097
\definecolor{VividPurple}{HTML}{500000}
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{2A2A2A}
\colorlet{heading}{VividPurple}
\colorlet{accent}{VividPurple}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}

% Change the bullets for itemize and rating marker
% for \cvskill if you want to
\renewcommand{\itemmarker}{{\small\textbullet}}
\renewcommand{\ratingmarker}{\faCircle}
\newcommand{\gitlab}[1]{\printinfo{\faGitlab}{#1}}

%% sample.bib contains your publications
\addbibresource{sample.bib}

\begin{document}
\name{Sam McDevitt}
\tagline{Junior at Mississippi State University}
\personalinfo{%
  % Not all of these are required!
  % You can add your own with \printinfo{symbol}{detail}
  \email{\href{mailto:sam1123@msstate.edu}{sam1123@msstate.edu}}
  \phone{(601)-668-6782}
  \location{Starkville, MS}
  \linkedin{\href{https://www.linkedin.com/in/sammcdevitt/}{https://www.linkedin.com/in/sammcdevitt/}} \
  \printinfo{\faShield}{U.S. Citizen}
}

%% Make the header extend all the way to the right, if you want. Extend the right margin by 8cm (=6.8cm marginparwidth + 1.2cm marginparsep)
\begin{adjustwidth}{}{-8cm}
\makecvheader
\end{adjustwidth}

%% Provide the file name containing the sidebar contents as an optional parameter to \cvsection.
%% You can always just use \marginpar{...} if you do
%% not need to align the top of the contents to any
%% \cvsection title in the "main" bar.


\cvsection[sidebar]{Experience}

\cvevent{Laboratory Teaching Assistant }{Mississippi State University - Department of Electrical and Computer Engineering}{January 2019 -- Present}{Starkville, MS}
\begin{itemize}
\item Assisted students with lab assignments using Microchip’s MPLAB, the PIC24, and assembly programming 
\item Experienced with debugging other peoples code and hardware in order to help students submit a working lab. 
\end{itemize}

\divider

\cvevent{Undergraduate Researcher}{Mississippi State University - Institute for Clean Energy Technologies}{August 2017 -- Present}{Starkville, MS}
\begin{itemize}
\item Designed, printed, assembling, and debugging circuit boards for remote system controls and powering autonomous robots.  
\item Developed firmware in C for system controls through the Microchip IDE. 
\item Improved radiation detector readings by writing python scripts to record data. 
\end{itemize}
\divider

\cvevent{Computer Engineering Intern}{Kopis Mobile}{May 2017 -- August 2017}{Flowood, MS}
\begin{itemize}
\item Simplified inventory management by creating a python program that could create inventory items in a database and in an Orcad library by web scrapping. 
\item Updated and fixed errors within tables of an Odoo ERP inventory database. 
\item Integrated the ERP database into SolidWorks by creating an add-in that would pull 3D models from the database, and place the parts in the SolidWorks assembly project

\end{itemize}

\cvsection{Leadership Experience}
% https://github.com/liantze/AltaCV/blob/0bafa18846c7651bc8c5a9215685d4c56fba5f84/altacv.cls#L131
% https://www.sharelatex.com/learn/Hyperlinks
\cvproject{}{Electrical and Computer Engineering Ambassador - Vice Chair}
\begin{itemize}
\item Liaison between department and students
\item Provide lab tours for visiting groups and potential students 
\item Meet with ECE Department Advisory board faculty candidates.
\end{itemize}

\cvproject{}{IEEE Publicity Chair and Recruiting Coordinator}
\begin{itemize}
\item Designed flyers and advertise IEEE events. 
\item Recruit new students to join the Mississippi State Chapter of IEEE
\end{itemize}

\cvproject{}{First Technical Challenge Judge}
\begin{itemize}
    \item Interviewed teams at FIRST competitions in order to determine which team is the best fit for an award
    \item Determined which teams should be awarded with a panel of other judges. 
\end{itemize}

% \divider

% \cvevent{Product Engineer}{Google}{23 June 1999 -- 2001}{Palo Alto, CA}

% \begin{itemize}
% \item Joined the company as employee \#20 and female employee \#1
% \item Developed targeted advertisement in order to use user's search queries and show them related ads
% \end{itemize}

% \cvsection{A Work Day of My Life}

% Adapted from @Jake's answer from http://tex.stackexchange.com/a/82729/226
% \wheelchart{outer radius}{inner radius}{
% comma-separated list of value/text width/color/detail}
% \wheelchart{1.5cm}{0.5cm}{%
%   10/13em/accent!30/Business Planning and Strategy implementation, 
%   25/9em/accent!60/Resolving issues with project teams \& stakeholders,
%   5/12em/accent!10/Budget Management, 
%   20/12em/accent!40/Stakeholder Management,
%   5/8em/accent!20/In-House Business development,
%   30/9em/accent/Leading and motivating project members that their work has meaning,
%   5/8em/accent!20/Networking
% }


\clearpage


\end{document}
